The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-04-01 doc/paper/paper2d.tex
Updated figures

>>>>

\begin{figure}[tb]
\figurenum{8}
\epsscale{1.0}
\plotone{spDiag2d-0412-52258_156.eps}
\figcaption{An example of 1-d sky subtraction for camera r1 on SDSS
plate 412.  The top panel shows data from 16 sky fibers corrected to airmass
unity with vertical extent equal to 67\% errors.  The solid red line shows
the best fit B-spline, with only wavelength as an independent variable.
The bottom panel shows the residual of the fit in flux counts in the sky 
spectra.
\label{fig8}
}
\end{figure}

\begin{figure}[tb]
\figurenum{9}
\epsscale{1.0}
\plotone{spDiag2d-0412-52258.ps_153}
\figcaption{An example of the wavelength corrections to match expected 
sky emission line wavelength centers in a single r1 exposure.  The position
residuals in spectral pixels are shown as measurements of 12 sky 
emission lines for all 320 fibers.  The red positions show the initial 
predicted positions based on the arc-lamp wavelength solutions, and the green
positions are based on the updated solution after shifting and stretching to
match the observed sky lines positions.  The residuals can be compared to a
full pixel in the top left corner, and are much smaller than 5\%.
\label{fig9}
}
\end{figure}
